Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-20 article.tex
wordings

We will compare our approach to the Pearson correlation (see Section
\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
\begin{itemize}
\item \textbf{GTE} \citep{stetter2012model}
, the baseline of the challenge, measures for all pairs of
neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
$i$ given the observation of the time series of the neuron $j$
conditionally to the observation of past time series of neuron $i$,
whenever the average fluorescence is over a conditioning level.
Pre-processing and conditioning level were set to reproduce baseline of the
challenge.

@@

If the undirected network is perfectly inferred, it would already yield
high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
to infer edge directivity is likely to be counter-productive or yield
small gain.
By contrast, the same experiment with AUPRC would yield
to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
correctly directivity would be more rewarding in AUPRC term.
Interestingly, methods that takes into account directivity, namely GTE and
GENIE3, slightly improve their AUROC and AUPRC by giving the same way to directed edges.
(see GTE and GTE(undirected) in Figure \ref{fig:curves}
\textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
especially pr-curve.}).
Trying to detect the link direction is more penalizing than rewarding.

>>>>

The proposed approach is compared to Pearson correlation statistics (as
described in Section~\ref{sec:inference}), generalized transfer entropy (GTE)
and the GENIE3 algorithm.
\begin{itemize}
\item \textbf{GTE} \citep{stetter2012model}, the baseline of the challenge, measures for all pairs of
neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
$i$ given the observation of the time series of the neuron $j$
conditionally to the observation of past time series of neuron $i$,
whenever the average fluorescence is over a conditioning level.
Pre-processing and conditioning level were set to reproduce baseline of the
challenge.

@@

If the undirected network is perfectly inferred, it would already yield
high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
to infer edge directivity is likely to be counter-productive or yield
small gain.
By contrast, the same experiment with AUPRC would yield
to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
correctly directivity would be more rewarding in AUPRC term.
Interestingly, methods that takes into account directivity, namely GTE and
GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
(see GTE and GTE(undirected) in Figure \ref{fig:curves}
\textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
especially pr-curve.}).
Trying to detect the link direction is more penalizing than rewarding.
